%-------------------------
% Jessica Carneiro Resume
%-------------------------
\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

\input{glyphtounicode.tex}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Colours
\definecolor{accent}{RGB}{31,78,121}
\definecolor{subaccent}{RGB}{46,117,182}
\definecolor{lightgray}{RGB}{89,89,89}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\color{accent}\bfseries\large
}{}{0em}{}[\color{subaccent}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{accent}#1} & \small\color{lightgray}#2 \\
      \textit{\small\color{subaccent}#3} & \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.05in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\newcommand{\achievementItem}[1]{
  \item[\color{subaccent}$\triangleright$]\small{\color{lightgray}#1 \vspace{-2pt}}
}

%==============================
\begin{document}

%---------- HEADER ----------
\begin{center}
  {\Huge\bfseries\color{accent} J\'ESSICA CARNEIRO} \\[6pt]
  \small
  \hspace{6pt}$|$\hspace{6pt}
  \href{https://www.linkedin.com/in/jessicacarneiro}{\faLinkedin linkedin.com/in/jessicacarneiro}
  \hspace{6pt}$|$\hspace{6pt}
  \href{https://github.com/jessicacarneiro}{\faGithub github.com/jessicacarneiro}
  \\[4pt]
  {\small\color{subaccent}\bfseries DevOps Engineer \quad|\quad SRE \quad|\quad Backend Software Engineer}
\end{center}

%---------- PROFESSIONAL SUMMARY ----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.2in, itemsep=1pt, parsep=0pt]
  \resumeItem{Backend engineer with 7+ years of experience building scalable, high-availability systems in Java and Kotlin, currently transitioning into DevOps/SRE.}
  \resumeItem{Hands-on experience with cloud infrastructure (AWS), CI/CD pipelines, Infrastructure as Code (Terraform/Terragrunt), and container orchestration (Kubernetes, Docker).}
  \resumeItem{Strong background in asynchronous messaging (Kafka, AWS SQS/SNS) and observability tooling (New Relic, Datadog).}
  \resumeItem{Proven track record in improving system reliability, reducing operational failures, and automating processes across engineering teams.}
\end{itemize}

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.05in, label={}, itemsep=2pt, parsep=0pt]
  \small\item\textbf{Languages:} Java, Kotlin, Python, Bash, TypeScript, JavaScript, C\#
  \small\item\textbf{Frameworks \& Tools:} Spring Boot, Quarkus, Ktor, Django, Fastify, FastAPI, Flask, NodeJS, GraphQL
  \small\item\textbf{Cloud \& Infra:} AWS, Terraform, Terragrunt, Docker, Kubernetes, ArgoCD, GitOps
  \small\item\textbf{CI/CD:} CircleCI, GitHub Actions, Azure DevOps, Jenkins, GoCD
  \small\item\textbf{Messaging \& Observability:} Kafka, AWS SQS/SNS, Datadog, New Relic
  \small\item\textbf{Databases:} PostgreSQL, MongoDB, MySQL, Redis
\end{itemize}

%---------- PROFESSIONAL EXPERIENCE ----------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading{Navalia}{Jul 2025 -- Present}{DevOps Engineer --- Platform Team}{}
  \resumeItemListStart
    \resumeItem{Design and maintain deployment pipelines ensuring consistent and reliable infrastructure provisioning.}
    \resumeItem{Author Bash scripts to automate repetitive tasks (e.g., config generation), reducing manual errors and engineering toil.}
    \resumeItem{Apply GitOps principles to manage infrastructure and application state across Kubernetes clusters.}
  \resumeItemListEnd
  \begin{itemize}[leftmargin=0.2in, itemsep=1pt, parsep=0pt]
    \small\item\textbf{\color{lightgray}Key Achievements}
  \end{itemize}\vspace{-6pt}
  \begin{itemize}[leftmargin=0.3in, itemsep=1pt, parsep=0pt]
    \achievementItem{Improved pipeline error feedback for developers, significantly reducing debugging time.}
    \achievementItem{Strengthened security checks in CI/CD pipelines across the platform.}
  \end{itemize}

  \resumeSubheading{Shippo}{Oct 2024 -- Apr 2025}{Software Engineer --- Labels Team}{}
  \resumeItemListStart
    \resumeItem{Developed and maintained backend services in Python/Django for shipping label generation across multiple carriers.}
    \resumeItem{Integrated new shipping carriers via REST APIs, expanding platform coverage.}
    \resumeItem{Contributed to performance, resilience, and scalability improvements in label processing systems.}
    \resumeItem{Collaborated with the infrastructure team to create monitoring alerts via Terraform.}
    \resumeItem{Built New Relic monitoring dashboards to ensure operational reliability.}
  \resumeItemListEnd

  \resumeSubheading{Navalia}{Jan 2023 -- Oct 2024}{Senior Consultant Software Engineer}{}
  \resumeItemListStart
    \resumeItem{Led backend development on large-scale microservices projects using Java and Kotlin.}
    \resumeItem{Implemented CI/CD pipelines with CircleCI and GitHub Actions; automated infrastructure with Terraform and Terragrunt.}
    \resumeItem{Contributed to a Kubernetes migration, working with infrastructure teams on deployment strategy and scalability.}
    \resumeItem{Drove asynchronous messaging solutions via Kafka and application monitoring with Datadog.}
    \resumeItem{Championed DevOps best practices adoption within development squads.}
  \resumeItemListEnd

  \resumeSubheading{Hotmart}{Nov 2021 -- Jan 2023}{Back-end Developer}{}
  \resumeItemListStart
    \resumeItem{Built REST APIs with Java and Spring Boot, focusing on high availability and scalability.}
    \resumeItem{Implemented CI/CD pipelines and Infrastructure as Code practices using Terraform.}
    \resumeItem{Worked within agile squads (Scrum/Kanban) with strong emphasis on test automation and continuous improvement.}
  \resumeItemListEnd

  \resumeSubheading{Gympass}{Aug 2021 -- Nov 2021}{Backend Engineer}{}
  \resumeItemListStart
    \resumeItem{Developed backend services using Kotlin, Spring Boot, TypeScript, NodeJS, GraphQL, PostgreSQL, ArgoCD, and Kubernetes.}
  \resumeItemListEnd

  \resumeSubheading{ThoughtWorks}{Mar 2020 -- Jul 2021}{Consultant Software Developer}{}
  \resumeItemListStart
    \resumeItem{Contributed to digital transformation projects, building microservices in Java and Kotlin.}
    \resumeItem{Completed ThoughtWorks University, an intensive program in agile practices, software engineering, and modern infrastructure.}
    \resumeItem{Implemented CI/CD pipelines with Azure DevOps, ensuring code quality, test coverage, and automated deployments.}
    \resumeItem{Collaborated with international clients to deliver resilient, scalable solutions.}
  \resumeItemListEnd

  \resumeSubheading{Blip}{Jun 2019 -- Jan 2020}{Software Engineer}{}
  \resumeItemListStart
    \resumeItem{Developed chatbot solutions on the Blip platform using C\# and .NET, delivering conversational experiences for clients.}
    \resumeItem{Collaborated with product and design teams via Azure DevOps, contributing to continuous delivery of chatbot features.}
    \resumeItem{Built integrations using JavaScript to connect chatbot flows with APIs.}
  \resumeItemListEnd

  \resumeSubheading{UFMG --- Computer Science Department}{May 2017 -- May 2018}{Undergraduate Research Intern}{}
  \resumeItemListStart
    \resumeItem{Conducted research on security protocols for IoT, focusing on federated identity management and post-quantum cryptography.}
    \resumeItem{Co-designed and implemented FLAT (Federated Lightweight Authentication of Things), a novel authentication protocol for resource-constrained IoT devices}
    \resumeItem{Prototyped and validated FLAT on Arduino hardware, demonstrating feasibility on devices with minimal computational resources.}
    \resumeItem{Co-authored two peer-reviewed publications: a conference paper (SBSeg 2019) and a journal article (\textit{Ad Hoc Networks}, Elsevier, 2020).}
  \resumeItemListEnd

  \resumeSubheading{CI\&T}{Feb 2017 -- May 2017}{Software Engineer Intern}{}
  \resumeItemListStart
    \resumeItem{Completed structured training in Java, TDD, HTML, CSS, and JavaScript.}
    \resumeItem{Contributed to internal web projects using Python, Angular, and Google Cloud Platform (GCP).}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\color{accent}B.Sc. in Computer Science --- UFMG (Federal University of Minas Gerais)} & \small\color{lightgray}2018 \\
    \small\color{lightgray}Exchange Program --- SUNY Old Westbury, New York, USA (Science without Borders) & \small\color{lightgray}2015--2016 \\
  \end{tabular*}
\resumeSubHeadingListEnd

%---------- PUBLICATIONS ----------
\section{Publications}
\begin{itemize}[leftmargin=0.05in, label={}, itemsep=4pt, parsep=0pt]
  \small\item Santos, M.L.B.A., \textbf{Carneiro, J.C.}, et al. ``FLAT: Federated Lightweight Authentication for the Internet of Things.'' \textit{Ad Hoc Networks}, Elsevier, 2020.
  \small\item Santos, M.L.B.A., \textbf{Carneiro, J.C.}, et al. ``A Federated Lightweight Authentication Protocol for the Internet of Things.'' \textit{Brazilian Symposium on Information and Computational Systems Security (SBSeg)}, 2019.
\end{itemize}

\end{document}
